### 2015-06-22 Manuscript/SW_early_life_telomeres_SOM_v9.Rmd
Added model selection table, removed logistic regression table (as now doing survival analysis instead)

@@

```{r Figure S4,fig.width=5,fig.height=5}
glm1 <- glm(SurvivedNext ~ Sex + Condition + TLKB + Insect + Ageclass + TLKB + GroupSize,
            data = FlSAall,
            family = 'binomial')
glm1 <- standardize(glm1)
glm2 <- dredge(glm1)
glm2avg <- model.avg(glm2, subset = delta <=6)
myimp2 <- importance(glm2avg)

#Make into a nice table
table2 <- imptable(glm2avg,myimp2)
table2 <- signif(table2,2)

#Sort out row names
nams <- rownames(table2)
nams[nams == 'c.Ageclass'] <- 'Age class'
nams[nams == 'z.Condition'] <- 'Body condition'
nams[nams == 'c.Sex'] <- 'Sex'
nams[nams == 'z.Insect'] <- 'Food av.'
nams[nams == 'z.TQspace'] <- 'TQ'
nams[nams == 'z.TLKB'] <- 'TL'
nams[nams == 'z.GroupSize'] <- 'Local density'
nams[nams == 'z.Insect:z.TLKB'] <- 'TL x Food av.'

rownames(table2) <- nams
colnames(table2) <- c('Estimate','SE','2.5%','97.5%','RI')

table2 <- data.frame(table2,myx=row.names(table2))

forestplot(table2)

**Figure S4** Model averaged estimates and confidence intervals (points and error bars, respectively) for all explanatory terms used in a generalised linear model with a binomial error structure and survival to adulthood as the response. Numbers in brackets are the relative importance of each term in the top model set (see main text for details). Food av = annual food availability, TL = telomere length TQ = territory quality.

>>>>

**Table S1** Model selection table for analysis of factors affecting early life telomere length in juvenile Seychelles warblers. Only models that remained in the top model set for model averaging (AICc $\leq$ 6 compared to the top model) are included here. i = intercept.

```{r Table S1}

#Run the model
lm1 <- lmer(TLKB ~ TQspace + Insect + GroupSize + Sex + Condition + Helper + (1|LayYear),
            data = FlSAall,REML=FALSE)

lm1 <- standardize(lm1)

#Model averaging
lm2 <- dredge(lm1)
t1 <- as.matrix(subset(lm2, delta<=6))
colnames(t1)[2:7] <- c('Sex', 'Body condition','Group size','Helper','Food av.','TQ')
getterms <- function(x)
  {
  temp <- c('i',names(which(!(is.na(x[2:7])))))
  return(paste(temp,collapse = " + "))
  }

tableS1 <- data.frame(Model = apply(t1,1,getterms),t1[,c('df','AICc','delta','weight')])
colnames(tableS1) <- c('Model','df','AICc', 'Delta AICc','Weight')
rownames(tableS1) <- NULL
tableS1$Model[tableS1$Model == ''] <- 'Null model'
kable(tableS1,digits=3)

@@
